ODGI: understanding pangenome graphs

### 2021-08-11 manuscript/main.tex
andrea for view
update authors section

\title[short Title]{ODGI: understanding pangenome graphs}
\author[Heumos, \textit{et~al}.]{
Andrea Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon Heumos\,$^{\text{\sfb 2} \dagger}$,
Pjotr Prins\,$^{\text{\sfb 3}}$,
and Erik Garrison\,$^{\text{\sfb 3}*}$
}

\address{
$^{\text{\sf 1}}$University of Tor Vergata, Rome, Italy and \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

@@

>>>>

\title[short Title]{ODGI: understanding pangenome graphs}
\author[Heumos, \textit{et~al}.]{
Andrea Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon Heumos\,$^{\text{\sfb 2} \dagger}$,
Sven Nahnsen\,$^{\text{\sfb 2}}$,
Pjotr Prins\,$^{\text{\sfb 3}}$,
and Erik Garrison\,$^{\text{\sfb 3}*}$
}

\address{
$^{\text{\sf 1}}$University of Tor Vergata, Rome, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

@@

% pjotr & andrea
